### 2022-09-15 chapters/benchmarking/conclusion.tex
refactoring

%% maybe add extension as a part of the conclusion for this chapter 
\section{Extension}\label{sec:bench_extension}
We propose to extend the benchmarking framework suggested by the \emph{Collaboratory on Experimental Evaluation of Software and Systems in Computer Science}\footnote{\url{http://evaluate.inf.usi.ch/}} to address those limitations.
Instead of only presenting the four primary aspects of their guidelines that were mentioned previously in section ~\ref{sec:benchmarking_reproducibility}, we propose an abstract model to describe an empirical experiment:

@@

% \begin{figure}%[!htb]
%     \center{\includegraphics[width=.9\linewidth]{imgs/JunitSonarplugin}}
%     \caption{Example of the Junit Sonar Plugin}\label{fig:sonar_plugin}
% \end{figure}
\section{Conclusion}

>>>>

%% maybe add extension as a part of the conclusion for this chapter 
\section{Benchmarking protocol to extend reproducibility}\label{sec:bench_extension}

We propose to extend the benchmarking framework suggested by the \emph{Collaboratory on Experimental Evaluation of Software and Systems in Computer Science}\footnote{\url{http://evaluate.inf.usi.ch/}} to address those limitations.
Instead of only presenting the four primary aspects of their guidelines that were mentioned previously in section ~\ref{sec:benchmarking_reproducibility}, we propose an abstract model to describe an empirical experiment:

@@

% \begin{figure}%[!htb]
%     \center{\includegraphics[width=.9\linewidth]{imgs/JunitSonarplugin}}
%     \caption{Example of the Junit Sonar Plugin}\label{fig:sonar_plugin}
% \end{figure}
\section{Conclusion \note{missing}}

### 2022-09-15 chapters/literature/draft_citations.tex
fix : compilation error
refactoring

% this sections containes all the references for each section :

% 1. group articles by field

@@

\begin{figure}
    \includegraphics[width=\linewidth]{imgs/cpu_cost_comparaison}
    \caption{electrical cost comparasion between two cpus }
    \label{fig:soa_comparaisoncpu}
\end{figure}

@@

we will place a greater emphasis on the software level in order to decrease the amount of energy that is used.more particularly on the execution phase of the program cycle.
We will be proceeding through an empirical analysis of the energy consumption of the software while changing some components of the source code without impacting its behavior.
In order to do this, we will elaborate a benchmarking process and a set of tools that are intended to assist practitioners in better comprehending and optimizing the energy usage of their applications.
Thus, we will begin by examining the state of the art of empirical analysis and retrieving the best empirical experimentation methodologies in the research field.Then, we will narrow these practices down to computer science so that we can finally adapt them to energy consumption.

@@

\subsubsection{Reproducibility}

>>>>

@@

\begin{figure}
    \includegraphics[width=\linewidth]{imgs/cpu_cost_comparaison}
    \caption{Electrical cost comparasion between two cpus }
    \label{fig:soa_comparaisoncpu}
\end{figure}

@@

We will place a greater emphasis on the software level in order to decrease the amount of energy that is used.more particularly on the execution phase of the program cycle.
We will be proceeding through an empirical analysis of the energy consumption of the software while changing some components of the source code without impacting its behavior.
In order to do this, we will elaborate a benchmarking process and a set of tools that are intended to assist practitioners in better comprehending and optimizing the energy usage of their applications.
Thus, we will begin by examining the state of the art of empirical analysis and retrieving the best empirical experimentation methodologies in the research field.Then, we will narrow these practices down to computer science so that we can finally adapt them to energy consumption.

@@

\subsubsection{Reproducibility}\label{subsec:soa_reproducibility}

### 2022-09-15 chapters/optimization/python-dir/python.tex
refactoring

\paragraph{Conclusion}
This study demonstrates that the optimal way to reduce the energy consumption of Python application is to follow the guidelines and to privilege the built-in functions.

\subsection{Python \& Multiprocessing}
\Cref{fig:python_multiprocessing} compares the behavior of python programs when we try to introduce parallelism.
As we know python is a single-threaded program thanks to the GLS (\emph{Global Lock System}) however, due to the increase in the number of cores/threads per CPU, many libraries started to take advantage of this hardware feature by simulating multithreading as multiple instances of the processor. % TODO: TO VERIFY

@@

\subsection{Python \& Machine Learning}
Machine learning is becoming an integral part of our daily lives, growing more potent and energy-hungry each year.
As machine learning can have a significant impact on climate change, it is vital to investigate mitigation techniques.

\paragraph{Hardware settings}
Chifflot 8 from Grid 5000's Lille site was used for all of the trials.
The machine is outfitted with two Intel Xeon Gold 6126 CPUs, each having 12 physical cores, 192 GB of RAM, and two 32 GB Tesla V100 GPUs.

\paragraph{Software settings}
For the sake of reproducibility, each experiment is done within a Docker container using Jupyter lab. These tests are run on top of a minimal version of Debian-10 to increase the accuracy of the tests by eliminating any unnecessary processes.

\subsubsection{Input Workload}
\paragraph{Models}
Several models were developed, however, only two were used in the final trials because they achieved 94 percent accuracy in an acceptable length of time.
David Page's cifar10-fast~\footnote{\url{https://github.com/davidcpage/cifar10-fast}} and Woonhyuk Baek's torch skeleton~\footnote{\url{https://github.com/wbaek/torchskeleton}} are shown here.

@@

\section{Results \& Findings}
As the model's accuracy increases, so does the energy required for the next accuracy increment.

@@

\paragraph{Conclusion}
We discovered that when the model's accuracy improves, so does the energy required for a subsequent accuracy gain.
This begs the question of when we should discontinue training.
Is a 10\% increase in accuracy worth it if we have to spend three times the energy?
Even while utilizing a GPU consumes more total power, the training time is significantly reduced.
As a result, the utilization of a GPU is required to lower the energy consumption of the training.
Some experiments revealed unusual behavior that was not studied during this internship.
These could be examined in future studies and perhaps used to achieve more energy savings.
The execution time did not depend on the number of cores employed in several studies.
This parameter had a significant impact on training time in others.
As a result, the best core configuration will be determined by the script.
The next steps in this area could include exploring the reasons for these discrepancies and possibly creating a script that can automatically find the ideal core configuration for a specific script.

\input{python_interperters.tex}
%% TODO : ADD General conclusion for the chapter

>>>>

\subsection{Conclusion}
This study demonstrates that the optimal way to reduce the energy consumption of Python application is to follow the guidelines and to privilege the built-in functions.

\section{Python \& Multiprocessing}
\Cref{fig:python_multiprocessing} compares the behavior of python programs when we try to introduce parallelism.
As we know python is a single-threaded program thanks to the GLS (\emph{Global Lock System}) however, due to the increase in the number of cores/threads per CPU, many libraries started to take advantage of this hardware feature by simulating multithreading as multiple instances of the processor. % TODO: TO VERIFY

@@

\section{Python \& Machine Learning}
Machine learning is becoming an integral part of our daily lives, growing more potent and energy-hungry each year.
As machine learning can have a significant impact on climate change, it is vital to investigate mitigation techniques.
\subsection{Experimental Protocol}
\subsubsection{Measurement context}
\paragraph{Hardware settings}
Chifflot 8 from Grid 5000's Lille site was used for all of the trials.
The machine is outfitted with two Intel Xeon Gold 6126 CPUs, each having 12 physical cores, 192 GB of RAM, and two 32 GB Tesla V100 GPUs.

\paragraph{Software settings}
For the sake of reproducibility, each experiment is done within a Docker container using Jupyter lab. These tests are run on top of a minimal version of Debian-10 to increase the accuracy of the tests by eliminating any unnecessary processes.
\subsubsection{Input Workload}
\paragraph{Models}
Several models were developed, however, only two were used in the final trials because they achieved 94 percent accuracy in an acceptable length of time.
David Page's cifar10-fast~\footnote{\url{https://github.com/davidcpage/cifar10-fast}} and Woonhyuk Baek's torch skeleton~\footnote{\url{https://github.com/wbaek/torchskeleton}} are shown here.

@@

\subsection{Results \& Findings}
As the model's accuracy increases, so does the energy required for the next accuracy increment.

@@

\subsection{Conclusion}
We discovered that when the model's accuracy improves, so does the energy required for a subsequent accuracy gain.
This begs the question of when we should discontinue training.
Is a 10\% increase in accuracy worth it if we have to spend three times the energy?
Even while utilizing a GPU consumes more total power, the training time is significantly reduced.
As a result, the utilization of a GPU is required to lower the energy consumption of the training.
Some experiments revealed unusual behavior that was not studied during this internship.
These could be examined in future studies and perhaps used to achieve more energy savings.
The execution time did not depend on the number of cores employed in several studies.
This parameter had a significant impact on training time in others.
As a result, the best core configuration will be determined by the script.
The next steps in this area could include exploring the reasons for these discrepancies and possibly creating a script that can automatically find the ideal core configuration for a specific script.

\input{python_interperters.tex}
\subsection{threads to validity \note{missing}}
\section{Conclusion \note{missing}}
